Exploring Bounds

### 2015-04-09 draft.tex
added notes

HELLO!

%First explore linear programming bound
Krawtouck polynomials

>>>>

\section{Introduction}

There exists a considerable interest today in determining the maximum possible
number of codewords for a code with certain parameters.  We use the notation $A_q(n,d)$
and $B_q(n,d)$, defined as the maximum of number of codewords in a code over
$\mathbb{F}_q$ of length $n$ and minimum distance $d$ for an arbitrary (linear
on non-linear) code and linear code, respectively.  In lecture, we have
considered upper bounds---Sphere Packing, Singleton, and Greismer---as well as
lower bounds---Gilbert and Varshamov---on these values.  The purpose of this
paper is to consider other well-known bounds in the literature.

This paper is broken up into $x$ sections.

%First explore linear programming bound
Asymptotic singleton, include 2 examples
Asymptotic plotkin, some examples
draw graph
Asymptotic hamming
	define hilbert, prove 135,136, define vq(n,a),
	black box 2.10.3, prove 2.10.5
